%
% Machine Learning Course Homework1
% Only available in ZJU
%
\documentclass[12pt,twoside]{article}

\input{macros}

\usepackage{amsmath}
\usepackage{url}
\usepackage{mdwlist}
\usepackage{graphicx}
\usepackage{clrscode3e}
\newcommand{\isnotequal}{\mathrel{\scalebox{0.8}[1]{!}\hspace*{1pt}\scalebox{0.8}[1]{=}}}
\usepackage{listings}
\usepackage{tikz}
\usetikzlibrary{arrows}
\usetikzlibrary{matrix}
\usetikzlibrary{positioning}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{shapes.misc}
\usetikzlibrary{trees}

\newcommand{\answer}{
 \par\medskip
 \textbf{Answer:}
}

\newcommand{\collaborators}{ \textbf{Collaborators:}
%%% COLLABORATORS START %%%

\tabT Name: Junlin Yin

\tabT Student ID: 3160104340
%%% COLLABORATORS END %%%
}

\newcommand{\answerIa}{ \answer
%%% PROBLEM 1(a) ANSWER START %%%
\begin{enumerate}
\item Given the size of testing set 1000:\\
When the size of training set is 10, training error rate: 0, testing error rate: 10.9\%;\\
When the size of training set is 100, training error rate: 0.146\%, testing error rate： 1.38\%.
\item Given the size of testing set 1000:\\
When the size of training set is 10, average number of iterations: 52;\\
When the size of training set is 100, average number of iterations: 2241.
\item Given the size of testing set 1000:\\
The Perceptron Machine will iterate infinitely if the maximum number of iterations is not defined.\\
The training error cannot reach zero, and the testing error is much higher than that in linearly separatable cases.
\end{enumerate}
%%% PROBLEM 1(\item d) ANSWER END %%%
}

\newcommand{\answerIb}{ \answer
%%% PROBLEM 1(b) ANSWER START %%%
\begin{enumerate}
\item Given the size of testing set 1000:\\
The training error rate: 3.89\%, the testing error rate: 4.68\%.
\item Given the size of testing set 1000:\\
The training error rate: 13.1\%, the testing error rate: 14.3\%.
\item The training error rate: 49.0\%, the testing error rate: 55.0\%.
\item The training error rate: 5.00\%, the testing error rate: 6.60\%.
\end{enumerate}
%%% PROBLEM 1(b) ANSWER END %%%
}

\newcommand{\answerIc}{ \answer
%%% PROBLEM 1(c) ANSWER START %%%
Here is the breif derivation of the logistic gradient:
As the question suggests, the likelihood function can be presented as:
$$P(y|x, \omega) = \hat{y}^y*(1-\hat{y})^{1-y}$$
where $\hat{y} = \frac{1}{1+\exp{[-\omega^Tx]}}$, so the total-log-likelihood function is:
\begin{displaymath}
    \begin{aligned}
    L &= \sum\limits_{i=1}^{m}l_i\\
    &= \sum\limits_{i=1}^{m}y^{(i)}\log{\hat{y^{(i)}}}+(1-y^{(i)})\log{(1-\hat{y^{(i)}})}
    \end{aligned}
\end{displaymath}
where $m$ is the number of samples. Thus we can define the loss function as the minus log-likelihood function,
 so the gradient is:
 \begin{displaymath}
    \begin{aligned}
    \nabla_\omega J &= -\frac{\partial}{\partial\omega}L\\
    &= \sum\limits_{i=1}^{m}\frac{\hat{y^{(i)}} - y^{(i)}}{\hat{y^{(i)}}(1-\hat{y^{(i)}})}*\frac{\partial\hat{y^{(i)}}}{\partial \omega}\\
    &= \sum\limits_{i=1}^{m}x^{(i)}*(\hat{y^{(i)}} - y^{(i)})\\
    &= [\hat{y} - y]X^T
    \end{aligned}
\end{displaymath}
Based on this:
\begin{enumerate}
    \item Given the size of testing set 1000:\\
    The training error rate: 0.29\%, the testing error rate: 1.09\%.
    \item Given the size of testing set 10000:\\
    The training error rate: 11.8\%, the testing error rate: 12.8\%.       
\end{enumerate}
%%% PROBLEM 1(c) ANSWER END %%%
}

\newcommand{\answerId}{ \answer
%%% PROBLEM 1(d) ANSWER START %%%
\begin{enumerate}
    \item Given the size of testing set 1000:\\
    The training error rate: 0, the testing error rate: 3.36\%.
    \item Given the size of testing set 1000:\\
    The training error rate: 0, the testing error rate: 1.03\%. 
    \item Average number of support vectors: 3.5.  
\end{enumerate}
%%% PROBLEM 1(d) ANSWER END %%%
}

\newcommand{\answerIIa}{ \answer
%%% PROBLEM 2(a) ANSWER START %%%
\begin{enumerate}
    \item According to LOOCV, the optimal lambda is 10.
    \item When $\lambda=0$, $\sum\limits_{i=0}^{P}\omega_i^2=14.6$; 
    when $\lambda=10$, $\sum\limits_{i=0}^{P}\omega_i^2=1.23$.
    \item When $\lambda=0$, the training error is 0 and the testing error is 10.7\%; 
    When $\lambda=10$, the training error is 0 and the testing error is 7.23\%.
\end{enumerate}
%%% PROBLEM 2(a) ANSWER END %%%
}
\newcommand{\answerIIb}{ \answer
%%% PROBLEM 2(b) ANSWER START %%%
According to LOOCV, the optimal lambda is 0.001.\\
When $\lambda=0$, the training error is 0 and the testing error is 6.73\%; 
When $\lambda=0.001$, the training error is 0 and the testing error is 6.58\%.
%%% PROBLEM 2(b) ANSWER END %%%
}

\newcommand{\answerIIIa}{ \answer 
%%% PROBLEM 3(a) ANSWER START %%%
\begin{enumerate}
\item False. Once the model is defined, the bias is defined, too. It doesn't work no matter how 
many samples are added if the model is over-simple.
\item False. We don't like neither high-bias and high-variance. Although models with high variance can
fit the training data perfectly, they don't generalize to testing data very well. However, high-variance
problems can be tackled by adding more training samples, which is likely to get further improvement
compared with high-bias cases.
\item True. When the parameters get more, there's a greater chance that training data are not enough, thus
creating too complicated models.
\item False. Regularization is used to mitigate over-fitting, where testing error will be reduced but training 
error will not necessarily. On the contrary, the training error will probably increase a little bit because
some mistakes may be allowed.
\item False. By using very large $\lambda$, the over-fitting penalty gets extremely huge, but the high-bias
penalty gets relatively small. Therefore, models with large $\lambda$ usually suffer from high-bias problem.
\end{enumerate}
%%% PROBLEM 3(a) ANSWER END %%%
}

\setlength{\oddsidemargin}{0pt}
\setlength{\evensidemargin}{0pt}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{0in}
\setlength{\textheight}{8.5in}

% Fill these in!
\newcommand{\theproblemsetnum}{2}
\newcommand{\releasedate}{May 16, 2019}
\newcommand{\partaduedate}{May 30, 2019}
\newcommand{\tabUnit}{3ex}
\newcommand{\tabT}{\hspace*{\tabUnit}}

\begin{document}

\handout{Homework \theproblemsetnum}{\releasedate}



\collaborators
% Please download the .zip archive for this problem set, and refer to the
% hw2.pdf file for instructions on preparing your solutions.
%


\medskip

\hrulefill

\begin{problems}

\problem \textbf{A Walk Through Linear Models}
\begin{problemparts}
\problempart Perceptron
\answerIa

\problempart Linear Regression
\answerIb

\problempart Logistic Regression
\answerIc

\problempart Support Vector Machine
\answerId
\end{problemparts}
\newpage

\problem \textbf{Regularization and Cross-Validation}
\begin{problemparts}
\problempart
Implement Ridge Regression and use LOOCV to tune...
\answerIIa

\problempart
Implement Logistic Regression and use LOOCV to tune...
\answerIIb

\end{problemparts}
\newpage
\problem \textbf{Bias Variance Trade-off}
\begin {problemparts}
\problempart True or False:
\answerIIIa
\end{problemparts}

\end{problems}
\end{document}
